Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2010-11-15 mnras.tex

\begin{figure}
  \plotone{fig/test2_ifront.eps}
  \caption{\label{fig:test2_2} Test 2. (\hii region expansion
    with a $T=10^5$ K blackbody spectrum).  Top: Evolution of the
    radius of the simulated ionization front (dashed) and analytical
    (solid) Str\"{o}mgren radius.  Bottom: The ratio of the calculated
    and analytical Str\"{o}mgren radius.}
\end{figure}

\begin{figure*}
  \epsscale{2}
  \plotone{fig/test2_slices}
  \epsscale{1}
  \caption{\label{fig:test2_3} Test 2. (\hii region expansion
    with a $T=10^5$ K blackbody spectrum).  Top: Slices through the
    origin of neutral fraction at 10 and 100 Myr.  Bottom: Slices of
    temperature at 10 and 100 Myr.}
\end{figure*}

@@

In Figure \ref{fig:test2_1}, we show the radially averaged neutral and
ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
neutral fraction of the domain.  Compared with Test 1, the ionization
front is thicker, as expected with the harder spectrum.  The total
neutral fraction decreases to 0.67 over 4$t_{\rm rec} = 500$ Myr,
which is in agreement with the analytical expectation and other codes
in RT06.  In Figure \ref{fig:test2_2}, we show the ratio of the
ionization front radius $r_{\rm IF}$ in our simulation and $R_s$.
Before $1.5t_{\rm rec}$, $r_{\rm IF}$ lags behind $R_s$, initially by
10\% and then increases to $R_s$; however afterwards, this ratio
asymptotes to a solution that is 4\% greater than $R_s$.  This
behavior is approximately the median result in RT06, where this ratio
varies between 1 and 1.1, and the early evolution of $r_{\rm IF}$ is
under-predicted by almost all of the codes.  If we use one energy
group with the mean energy (29.6 eV) of a $T=10^5$ K blackbody, we
find that $r_{\rm IF}/R_s$ = 1.08, which is representative of the
codes in the upper range of RT06.  In Figure \ref{fig:test2_3}, we
show slices of neutral fraction and temperature through the origin at
$t = $ 10 and 100 Myr.  Here one sees the spherically symmetric
\hii regions and a smooth temperature transition to the neutral
ambient medium.

>>>>

\begin{figure*}
  \epsscale{2}
  \plotone{fig/test2_slices}
  \epsscale{1}
  \caption{\label{fig:test2_2} Test 2. (\hii region expansion
    with a $T=10^5$ K blackbody spectrum).  Top: Slices through the
    origin of neutral fraction at 10 and 100 Myr.  Bottom: Slices of
    temperature at 10 and 100 Myr.}
\end{figure*}

\begin{figure}
  \plotone{fig/test2_ifront.eps}
  \caption{\label{fig:test2_3} Test 2. (\hii region expansion
    with a $T=10^5$ K blackbody spectrum).  Top: Evolution of the
    radius of the simulated ionization front (dashed) and analytical
    (solid) Str\"{o}mgren radius.  Bottom: The ratio of the calculated
    and analytical Str\"{o}mgren radius.}
\end{figure}

@@

In Figure \ref{fig:test2_1}, we show the radially averaged neutral and
ionized fraction at $t = $ 10, 30, 100, and 500 Myr, and the total
neutral fraction of the domain.  Compared with Test 1, the ionization
front is thicker, as expected with the harder spectrum.  The total
neutral fraction decreases to 0.67 over 4$t_{\rm rec} = 500$ Myr,
which is in agreement with the analytical expectation and other codes
in RT06.  In Figure \ref{fig:test2_2}, we show slices of neutral
fraction and temperature through the origin at $t = $ 10 and 100 Myr.
Here one sees the spherically symmetric \hii regions and a smooth
temperature transition to the neutral ambient medium.  In Figure
\ref{fig:test2_3}, we show the ratio of the ionization front radius
$r_{\rm IF}$ in our simulation and $R_s$.  Before $1.5t_{\rm rec}$,
$r_{\rm IF}$ lags behind $R_s$, initially by 10\% and then increases
to $R_s$; however afterwards, this ratio asymptotes to a solution that
is 4\% greater than $R_s$.  This behavior is approximately the median
result in RT06, where this ratio varies between 1 and 1.1, and the
early evolution of $r_{\rm IF}$ is under-predicted by almost all of
the codes.  If we use one energy group with the mean energy (29.6 eV)
of a $T=10^5$ K blackbody, we find that $r_{\rm IF}/R_s$ = 1.08, which
is representative of the codes in the upper range of RT06.
